Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex
One more challenge in "Challenges"

The challenges of introducing programmability into existing storage systems: (1) Programmability while keeping storage system available, (2) Finding and factoring out hard-wired policies and optimizations, (3) Bugs that were hidden because mechanisms were only exercised according to hard-wired policies and not in their full generality they were thought of -- programmability into a storage system turned out to be a great debugging tool.

@@

% straw man example
Keeping track of the state of a distributed system is an essential part of any 
successful service and a necessary component in order to diagnose and detect 
failures, when they occur. In the case of Ceph, a consistent view of cluster 
state among server daemons and clients is critical to provide strong consistency 
guarantees to clients. Ceph maintains cluster state information in per-subsystem 
``maps'' (e.g. OSD map, MDS map) that record membership and status information. 
A PAXOS-based monitoring service (termed, the Monitor) is responsible for 
integrating state changes into cluster maps, responding to requests from 
out-of-date clients and synchronizing members of the cluster whenever there is a 
change in a map so that they all observe the same system state. As a fundamental 
building block of many system designs, consensus abstractions such as PAXOS are 
a common technique for maintaining consistent data versions, and are a useful 
system to expose.

The default behavior of the monitor can be seen as a PAXOS-based notification 
system, similar to the one introduced in~\cite{burrows_chubby_2006}, allowing 
clients to identify when new values (termed epochs in Ceph) are associated to 
given maps. While Ceph does not expose this service directly, it does allow 
limited use by clients through a key-value service intended for low-volume, 
small size read-only configuration information. While a key-value service is 
generally useful, it doesn't provide many of the useful services hidden within 
the monitoring framework that would be required for applications with more 
demanding requirements, such as creating arbitrary maps or associating 
application-specific logic that can be executed for particular maps (or values 
in a map).

\paragraph*{Malacology:} Malacology exposes Ceph's PAXOS-based monitoring 
service by embedding a Lua VM in the monitors that implements a generic API for 
creating maps and associating arbitrary data to them. This API also allows 
clients to specify small snippets of Lua code that can be executed on monitors. 
As a consequence of this, applications can define simple but useful 
domain-specific logic to the PAXOS quorum, such as authorization control (just 
specific clients can write new values) or to trigger actions based on specific 
values (e.g. sanitize values). Since the monitor is intended to be out of 
high-performance I/O paths, a general guideline is to make use of this 
functionality infrequently and to assign small values to maps. Malacology itself 
makes use of this functionality to version object interfaces defined in OSDs 
(\S\ref{active-storage}) and load balancing policies in MDSs 
(\S\ref{malacology:mds}).

@@

While a full description of the CORFU system is beyond the scope of this
paper, we'll briefly describe the custom storage device interface, sequencer
service, and recovery protocol, and how these services are instantiated in the
Malacology framework.

@@

High-performance in CORFU is achived using a sequencer service that assigns
log positions to clients by reading from a volatile, in-memory counter which
can run at a very high throughput and at low-latency. And since the sequencer
is centralized, ensuring seiralizability in the common case is trivial.  The
primary challenge in CORFU is handling the failure of the sequencer in a way
that preserves correctness. Failure of the sequencer service in CORFU is
handled by a recovery algorithm that recomputes the new sequencer state using
an application-specific custom storage interface to discover the tail of the
log, while simulatenously invalidating stale client requests using an
epoch-based protocol.

@@

{\bf Sequencer interface.} The sequencer resource supports the ability to
\emph{read()} the current tail value as well get the \emph{next()} position in
the log which also atomically increments the tail position. We implement this
functionality as methods on ZLog inode resources. The primary challenge in
mapping the sequencer resource to the metadata service is handling
serialization correctly.

Initially we sought to directly model the sequencer service in Ceph as a
non-exclusive, non-cacheable resource, forcing clients to perform a round-trip
access to the resource at the authoratiave metadata server for the sequencer
inode.  Interestingly, we found that the capapbility system in Ceph uses a
strategy to reduce metadata service load by allowing multiple clients that
open a shared file to temporarily cache the inode resource, resulting in a
round-robin, best-effort batching behavior. When a single client is accessing
the sequencer resource it is able to cache state locally without interruption.

While unexpected, this discovery allowed us to explore an implementation
strategy that we had not previously considered. In particular, for bursty
clients, and clients that can tolerate increased latency, this mode of operation may
allow a system to achieve much higher throughput than a system with a
centralized sequencer service.
We utilize the programmability of the metadata service to define a new policy
for handling capabilities that controls the amount of time that clients are
able to cache the sequencer resource. This allows an administrator or
application to control the trade-off between latency and throughput beyond the
standard best-effort policy that is present in Ceph by default.

In Section~\cite{evaluation} we quantify the trade-offs of throughput and
latency for an approach based on a round-robin batching mode, and compare this
mode to one in which the metadata server mediates access to the sequencer
state when in it is being shared among multiple clients.

{\bf Balancing policies.}
As opposed to the batching mode for controlling access to the sequencer
resource, more predictable latency can be achieved by treating the sequencer
inode as a shared non-cacheable resource, forcing clients to make a round-trip
to the metadata service. However, the shared nature of the metadata service
may prevent the sequencer from achieving maximum throughput. To provide a
solution to this issue we have taken advantage of the programmability of the
metadata service load balancing to construct a service-specific load balancing
policy. As opposed to a generic balancing policy that may strive for uniform
load distribution, a ZLog-specific policy may utilize knowledge of inode types
to migrate the sequencer service to provisioned hardware during periods of
contention or high demand.

\subsubsection{Storage Interface}

The storage interface is a critical component in the CORFU design. Clients
independently map log positions that they have obtained from a sequencer
service (described in detail in the next seciton) onto storage devices, while
storage devices provide an intelligent \emph{write}-once, random \emph{read}
interface for accessing log entries. The key to correctness in CORFU lies with
the enforcement of up-to-date epoch tags on client requests; requests tagged
with out-of-date epoch values are rejected, and clients are expected to
request a new tail from the sequencer after refreshing state from an auxillary
service.  This mechanism forms the basis for sequencer recovery.

In order to repopulate the cached tail value during recovery of a sequencer,
the maximum position in the log must be obtained. To do this, the storage
interface exposes an additional \emph{seal} method that atomically installs a
new epoch value and returns the maximum log position that has been written.
Since the recovery protocol does not inform clients of a new epoch value until
the end of the process, the validity of the tail can be guaranteed despite the
iterative process of contacting storage devices.  Recovery of the sequencer
process itself may be handled in many ways, such as leader election using an
auxillary service such as PAXOS.

>>>>

The challenges of introducing programmability into existing storage systems: (1) Programmability while keeping storage system available, (2) Finding and factoring out hard-wired policies and optimizations, (3) Bugs that were hidden because mechanisms were only exercised according to hard-wired policies and not in their full generality they were thought of -- programmability into a storage system turned out to be a great debugging tool, (4) version control and propagation of updates throughout the system without interrupting production workloads, (5) ...

@@

% straw man example
Keeping track of the state of a distributed system is an essential part of any 
successful service and a necessary component in order to diagnose and detect 
failures, when they occur. In the case of Ceph, a consistent view of cluster 
state among server daemons and clients is critical
to provide strong consistency guarantees to clients. Ceph maintains cluster
state information in per-subsystem ``maps'' (e.g. OSD map, MDS map) that
record membership and status information. A PAXOS-based monitoring service is
responsible for integrating state changes into cluster maps, and responding to
requests from out-of-date clients. As a fundamental building block of many
system designs, consensus abstractions such as PAXOS are a common technique
for maintaining consistent data versions, and are a useful system to expose.

While Ceph does not expose this service directly, it does allow limited use by
clients through a key-value service intended for low-volume, small size
configuration information. Unfortunately, while a key-value service is
generally useful, it doesn't provide many of the useful services hidden within
the monitoring framework that would be required for applications with more
demanding requirements.

\paragraph*{Malacology:} Malacology exposes the monitoring service in two ways. 
First, Malacology APIs for object storage (\S\ref{active-storage}) and the MDS 
(\S\ref{malacology:mds}) have functions available to them that allow them to 
store application-specific data in the highly-available, consistent store 
associated to the Ceph monitors. As mentioned
Map modification for propogation of state. We allow applications to augment
these data structures with application-specific metadata. In order to keep the
size of these data structures small application state may be stored elsewhere
and the references stored within the data structure.

@@

While a full description of the CORFU system is beyond the scope of this
paper, we'll briefly describe the custom storage device interface, sequencer
service, and recovery protocol that form the core components of CORFU that we
implement within Malacology:

{\bf Sequencer.}
High-performance in CORFU is achived using a sequencer service that assigns
log positions to clients by reading from a volatile, in-memory counter which
can run at a very high throughput and at low-latency. And since the sequencer
is centralized, ensuring seiralizability in the common case is trivial.  The
primary challenge in CORFU is handling the failure of the sequencer in a way
that preserves correctness. Failure of the sequencer service in CORFU is
handled by a recovery algorithm that recomputes the new sequencer state using
an application-specific custom storage interface to discover the tail of the
log, while simulatenously invalidating stale client requests using an
epoch-based protocol.

{\bf Storage Interface.} The storage interface is a critical component in the
CORFU design. Clients independently map log positions onto storage devices,
while storage devices provide an intelligent \emph{write}-once, random
\emph{read} interface for accessing log entries. The key to correctness in
CORFU lies with the enforcement of up-to-date epoch tags on client requests;
requests tagged with out-of-date epoch values are rejected, and clients are
expected to request a new tail from the sequencer after refreshing state from
an auxillary service. This mechanism forms the basis for sequencer recovery.

{\bf Sequencer Recovery.}
In order to repopulate the cached tail value during recovery of a sequencer,
the maximum position in the log must be obtained. To do this, the storage
interface exposes an additional \emph{seal} method that atomically installs a
new epoch value and returns the maximum log position that has been written.
Since the recovery protocol does not inform clients of a new epoch value until
the end of the process, the validity of the tail can be guaranteed despite the
iterative process of contacting storage devices.  Recovery of the sequencer
process itself may be handled in many ways, such as leader election using an
auxillary service such as PAXOS.

@@

@@

{\bf Physical design.}
The next component of our design is the low-level configuration of the
sequencer inode type that achieves the correct semantics.  Initially we sought
to directly model the sequencer service in Ceph as a non-exclusive,
non-cacheable resource, forcing clients to perform a round-trip access to the
resource at the authoratiave metadata server for the inode representing the
sequencer.  Interestingly, we found that the capapbility system in Ceph uses a
strategy to reduce metadata service load by allowing multiple clients that
open a shared file to temporarily cache the inode resource, resulting in a
round-robin, best-effort batching behavior. When a single client is accessing
the sequencer resource it is able to cache state locally without interruption.

While unexpected, this discovery allowed us to explore an implementation
strategy that we had not previously considered. In particular, for bursty
clients and clients that can tolerate high latency, this mode of operation may
allow a system to achieve much higher throughput than a system with a
centralized sequencer service.

In Section we quantify the trade-offs of throughput and latency for an
approach based on a round-robin batching mode, and compare this mode to one in
which the metadata server mediates access to the sequencer state when in it is
being shared among multiple clients.

{\bf Capability policies.}
We use capabilitity policies in the metadata service to tune the amount of
time that clients may cache the sequencer resource. This allows us to control
the trade-off between latency and throughput beyond the standard best-effort
policy.

{\bf Balancing policies.}
While the metadata service is a shared resource, authority over metadata
resources can be physically moved between servers using a dynamic, ZLog-aware
policy expressed in Mantle. For instance, one or more metadata servers may be
dedicated to supporting ZLog sequencer load. When the system load is low all
resources are spread evenly, but non-ZLog resources may be migrated to
best-effort servers when sequencer performance suffers.

{\bf Recovery.}
What?
